An Exposition on the Propriety of Restricted Boltzmann Machines

### 2016-07-31 presentations/jsm2016/index.Rmd
sizing

---
title: "An Exposition on the Propriety of Restricted Boltzmann Machines"
author: http://bit.ly/jsm2016-rbm
ratio: 16x10
output:
  rmdshower::shower_presentation:
    self_contained: false
    theme: ribbon
    katex: true
    fig_caption: true
    css: style.css
bibliography: refs.bib
---
```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(ggplot2)
library(dplyr)
library(tidyr)

>>>>

---
title: "An Exposition on the Propriety of Restricted Boltzmann Machines"
author: http://bit.ly/jsm2016-rbm
ratio: 4x3
output:
  rmdshower::shower_presentation:
    self_contained: false
    theme: ribbon
    katex: true
    fig_caption: true
    css: style.css
bibliography: refs.bib
---
```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(ggplot2)
library(dplyr)
library(tidyr)
